---
title: "Lab 1"
output:
  pdf_document: default
  html_document: default
date: "2023-01-17"
---

```{r include=FALSE}
library(ggplot2)
library(mime)
library(htmltools)
```



# Q1 Functions

## rational function 1.5
```{r Function1}
a <- 1.25
b <- 1
c <- 1
d <- 1
x <- c(seq(0,40,0.001))
rational <- (a*x+c)/(b*x+d)

a2 <- 1
b2 <- 1.25
rational2 <- (a2*x+c)/(b2*x+d)
rational_plot <- as.data.frame(cbind(x, rational, rational2))

ggplot(rational_plot, aes(x)) +
  geom_line(aes(y = rational)) +
  geom_line(aes(y = rational2), colour = "blue")

```

## bell-shaped function 1.6
```{r}
e <- 3
f <- 5
bell <- exp((-(x-f)^2)/e)

e2 <- 7
bell2 <- exp((-(x-f)^2)/e2)
bell_plot <- as.data.frame(cbind(x, bell, bell2))

ggplot(bell_plot, aes(x)) +
  geom_line(aes(y = bell)) +
  geom_line(aes(y = bell2), colour = "blue")
  
```

## sigmoidal 1.7
```{r}
g <- 0.5
h <- 0.01

sigmoid <- (h*exp(g*x))/((h*exp(g*x))+(1-h))


g2 <- -0.5
h2 <- 0.99
sigmoid2 <- (h2*exp(g2*x))/((h2*exp(g2*x))+(1-h2))
sigmoid_plot <- as.data.frame(cbind(x, sigmoid, sigmoid2))

ggplot(sigmoid_plot, aes(x)) +
  geom_line(aes(y = sigmoid)) +
  geom_line(aes(y = sigmoid2), colour = "blue")
  
```

# Q2

```{r echo=FALSE}
knitr::include_graphics("lab1_Q2.pdf") 
```

```{r echo=FALSE, "page=2", out.extra="page=2"}
knitr::include_graphics("lab1_Q2.pdf")
```

```{r echo=FALSE, "page=3", out.extra="page=3"}
knitr::include_graphics("lab1_Q2.pdf")
```


#  Q3. Numerically solve

```{r echo=TRUE}
# parameters
I <- 1
B <- 1
M <- 0.1
DJ <- 0.5
DA <- 0.5

#variables
time <- seq(0, 50, 1)
J <- rep(0,length(time))
A <- rep(0,length(time))

# initial conditions
J[1] <- 3
A[1] <- 3

# solve
for(t in seq(1,length(time)-1,1)) {
  J[t+1]=(J[t]+I+B*A[t])*(1-M)*(1-DJ)
  A[t+1]=(A[t]+M*(J[t]+I+B*A[t])*(1-DA))
}

plot(time, J) +
  lines(A)
```

## Graduate students
a. Provide R code demonstrating the effect.
```{r}
J2 <- matrix(0, nrow=length(time), ncol=5)
A2 <- matrix(0, nrow=length(time), ncol=5)

# initial conditions

J2[1,1:5] <- 3
A2[1,1:5] <- 3

Im <- seq(1, 5, 1)

# solve
for(t in seq(1,length(time)-1,1)) {
  for(I in Im){
  J2[t+1,I]=(J2[t,I]+I+B*A2[t,I])*(1-M)*(1-DJ)
  A2[t+1,I]=(A2[t,I]+M*(J2[t,I]+I+B*A2[t,I])*(1-DA))
  }
}

#plot
matplot(as.data.frame(J2),type="l")
matplot(as.data.frame(A2),type="l")
```

b. Provide a short paragraph (3-5 sentences) discussing the ecological implications of
increasing juvenile immigration rate.

Increasing the juvenile immigration rate increases the populations of juvenile and adult mice. This then increases the rate of growth of both populations. As more individuals enter the juvenile population, there are more individuals to mature to adults and, therefore, more adults to birth additional juveniles. The result is a positive feedback loop. 

